Report On:\\SEGUE-1: An Unevolved Fossil Galaxy from the Early Universe - Frebel, Simon \& Kirby

### 2021-03-13 Phys 311/CTA/Paper/paper.tex
Final Draft. Maybe?

\title{Report On:\\SEGUE-1: An Unevolved Fossil Galaxy from the Early Universe}

@@

\section{Topic Background} \label{sec:background}

@@

@@

The authors of this paper made new spectrography measurements of six stars within SEGUE-1 using the Magellan/MIKE and Keck/HIRES
spectrographs focusing on the chemical enrichment process to better understand star formation in the very early universe. The six
stars that were chosen were the brightest stars in SEGUE-1 which allowed for high resolution spectrography. Using the spectrographs
the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, and neutron-capture elements.
The authors then compared this data to stars found in classical dSph galaxies and the Milky Way halo.
The detail for the measurements of each of the stars are listed in table 1. Due to the dim nature of the six starts the signal to
noise ratio (S/N) was only moderate with values between 20 and 50

@@

With the high resolution spectrograph data the authors were able to extrapolate the abundances of the various elements inside the stars.
In figure 1 the authors plotted the spectra of the 6 stars compared to two other known stars, the ultra low metal $CD -38^{\circ}245$
and the very bright, and much younger, Arcturus. The plots are listed in ascending order of metallicity from top to bottom.

@@

Using the spectrography data the authors also plotted abundance ratios [X/Fe] relative to the iron abundance [Fe/H] for the elements
that were measured. The dashed line at [X/Fe] = 0 indicates the ratio of the element in our Sun with positive values meaning higher
abundance and lower values indicating lower abundance, on a log scale. Notice that in all of the SEGUE-1 stars the abundance of
$\alpha$-elements such as Mg, Si, Ca, and Ti, are all above that of the Sun. Elements that are synthesized by other processes that
occur later in the timeline such as Al, Cr, and Mn, have consistent abundances lower than that of the Sun.

@@

Another indication of SEGUE-1's age is the enhanced [$\alpha$/Fe] values found in all the measured stars that are consistent with each other
and the initial birth cloud. Figure 3 shows enrichment behavior plots, [Fe/H] vs. [$\alpha$/Fe], for MW Halo stars, classical dSph galaxy stars, and SEGUE-1 stars.
The top plot in fig. 3 shows the general trend of how classical dSph galaxies and MW Halo stars will appear on the enrichment behavior plot.
The middle plot shows the spread of MW Halo stars which have a plateau in the [$\alpha$/Fe] until [Fe/H] $\approx -1$ at which point
the [$\alpha$/Fe] approaches 0 where [Fe/H] is almost at 0. The bottom plot of fig. 3 shows the enrichment behavior plot for dSph galaxy
stars (small black circles), the measured stars from SEGUE-1 (large red filled in circles from this article, and red crosshair from
previous papers), and some other candidate stars (blue square, green circles, and magenta circles). In this bottom plot we can see that
the classical dSph stars and some of the other candidate stars have a plateau but do slope down towards the [$\alpha$/Fe] = 0 line.
On the other hand, the 6 measured stars from SEGUE-1 all reside around the [$\alpha$/Fe] = 0.5 line, even past the point where MW
Halo starts to slope down on the [Fe/H] axis. The consistent [$\alpha$/Fe] values in SEGUE-1 stars suggest that after the initial
enrichment of the birth cloud there were no other enrichment events, such as type Ia supernovae, in SEGUE-1.

\begin{wrapfigure}{r}{0.4\textwidth}
    \begin{center}
        \includegraphics[width=0.38\textwidth]{neutron_cap.jpg}
    \end{center}
    \caption{Birds}
    \label{fig:neutron_cap}
\end{wrapfigure}

The final indicator of SEGUE-1's old age is the low abundance of neutron-capture elements in SEGUE's non-binary system stars,
which total to less than \(\sim 10^{-7} M_{\odot}\) for each element, indicate that there were no neutron-capture element producing
process, which produce \(\sim 10^{-4} M_{\odot}\) of neutron-capture elements per event, that occurred during the star formation phase.

@@

Future research points to observing a larger portion of SEGUE 1 stars. The six stars that were observed in this paper were deemed to
be the brightest in the ultra faint dwarf galaxy and only allowed for a moderate S/N values between 20 and 46. In order to observe the other, dimmer,
stars in SEGUE 1 we would require better telescopes to overcome the noise.

>>>>

\title{Report On:\\SEGUE-1: An Unevolved Fossil Galaxy from the Early Universe - Frebel, Simon \& Kirby}

@@

\section{Background} \label{sec:background}

@@

\begin{wrapfigure}{r}{0.3\textwidth}
    \begin{center}
        \includegraphics[width=0.29\textwidth]{location.jpg}
    \end{center}
    \caption{Black dots show the location of surveyed stars within SEGUE-1. The seven dots with red borders indicate the six stars
    observed in this study as well as one star that was observed in a previous study}
    \label{fig:loc}
\end{wrapfigure}

@@

The authors of this paper made new spectrography measurements of six stars within SEGUE-1, highlighted in figure ~\ref{fig:loc},
 using the Magellan/MIKE and Keck/HIRES
spectrographs focusing on the chemical enrichment process to better understand star formation in the very early universe. The six
stars that were chosen were the brightest stars in SEGUE-1 which allowed for high resolution spectrography. Using the spectrographs
the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, and neutron-capture elements.
The authors then compared this data to stars found in classical dSph galaxies and the Milky Way halo.
The detail for the measurements of each of the stars are listed in table 1. Due to the dim nature of the six starts the signal to
noise ratio (S/N) was only moderate with values between 20 and 50

@@

With the high resolution spectrograph data the authors were able to extrapolate the abundances of the various elements inside the stars.
In figure ~\ref{fig:spectra} the authors plotted the spectra of the 6 stars compared to two other known stars, the ultra low metal $CD -38^{\circ}245$
and the very bright, and much younger, Arcturus. The plots are listed in ascending order of metallicity from top to bottom.

@@

Using the spectrography data the authors also plotted in figure ~\ref{fig:elements} the abundance ratios [X/Fe] relative to the iron abundance [Fe/H] for the elements
that were measured. The dashed line at [X/Fe] = 0 indicates the ratio of the element in our Sun with positive values meaning higher
abundance and lower values indicating lower abundance, on a log scale. Notice that in all of the SEGUE-1 stars the abundance of
$\alpha$-elements such as Mg, Si, Ca, and Ti, are all above that of the Sun. Elements that are synthesized by other processes that
occur later in the timeline such as Al, Cr, and Mn, have consistent abundances lower than that of the Sun.

@@

Another indication of SEGUE-1's age is the enhanced [$\alpha$/Fe] values found in all the measured stars that are consistent with 
each other and the initial birth cloud. Figure ~\ref{fig:enrich} shows enrichment behavior plots, [Fe/H] vs. [$\alpha$/Fe],
for MW Halo stars, classical dSph galaxy stars, and SEGUE-1 stars. The top left plot in fig. ~\ref{fig:enrich} shows the general 
trend of how classical dSph galaxies and MW Halo stars will appear on the enrichment behavior plot.
The top right plot shows the spread of MW Halo stars which have a plateau in the [$\alpha$/Fe] until [Fe/H] $\approx -1$ at which point
the [$\alpha$/Fe] approaches 0 where [Fe/H] is almost at 0. The bottom plot of fig. ~\ref{fig:enrich} shows the enrichment behavior plot for dSph galaxy
stars (small black circles), the measured stars from SEGUE-1 (large red filled in circles from this article, and red crosshair from
previous papers), and some other candidate stars (blue square, green circles, and magenta circles). In this bottom plot we can see that
the classical dSph stars and some of the other candidate stars have a plateau but do slope down towards the [$\alpha$/Fe] = 0 line.
On the other hand, the 6 measured stars from SEGUE-1 all reside around the [$\alpha$/Fe] = 0.5 line, even past the point where MW
Halo starts to slope down on the [Fe/H] axis. The consistent [$\alpha$/Fe] values in SEGUE-1 stars suggest that after the initial
enrichment of the birth cloud there were no other enrichment events, such as type Ia supernovae, in SEGUE-1.

\begin{wrapfigure}{r}{0.4\textwidth}
    \begin{center}
        \includegraphics[width=0.38\textwidth]{neutron_cap.jpg}
    \end{center}
    \caption{Neutron-capture element abundance [Sr/H] and [Ba/H] within the six observed SEGUE-1 stars in this study 
    (filled in red circles), one previously studied SEGUE-1 star (empty red circle), MW Halo stars (small black dots),
    and the other candidate stars (cyan, green, and blue markers). The light dotted line at [X/H] = 0 represents the abundance
    of the respective element within the sun and the bold dashed line represents the average abundance of the respective element
    within the observed SEGUE-1 stars.}
    \label{fig:neutron_cap}
\end{wrapfigure}

The final indicator of SEGUE-1's old age is the low abundance of neutron-capture elements in SEGUE's non-binary system stars.
Outside of binary star systems neutron-capture elements are synthesized in events such as r-process events and 
population III supermassive stars undergoing s-processes nucleosynthesis ~\cite{Truran2002}. Population III stars are believed to exist in the 
very early universe but have not been directly observed while r-process events can be observed from mergers of neutron stars or
type II supernovae ~\cite{Truran2002}. The authors looked specifically at Sr and Ba for neutron capture elements. In figure ~\ref{fig:neutron_cap} 
we see neutron-capture element abundances [Sr/H]
and [Ba/H] for MW Halo stars, classical dSph galaxy stars, and SEGUE-1 stars. The spread is quite wide with a number of stars having
neutron-capture element abundances equal to, and even greater, than the Sun as well as stars with neutron-capture element abundances
almost to [X/H] = -6. We can see that one of the SEGUE-1 stars observed in this study has a neutron-capture element abundance within
[X/H] $\pm 0.5$ of our Sun while the other five observed in this study, as well as the one observed in a previous study, much lower at
around [Sr/H] $\approx -5$ and [Ba/H] $\approx -4.5$. The total abundance of neutron capture elements within the lower six SEGUE-1 stars,
five from this study plus one from the previous study, total to less than \(\sim 10^{-7} M_{\odot}\) for each element, which is orders
of magnitude lower than the \(\sim 10^{-4} M_{\odot}\) released by a single neutron-capture element producing event. This low abundance
indicates that aside from the neutron-capture elements released in the very early universe no other neutron-capture element synthesis
occurred within SEGUE-1.

\begin{wrapfigure}{r}{0.4\textwidth}
    \begin{center}
        \includegraphics[width=0.38\textwidth]{carbon.jpg}
    \end{center}
    \caption{Neutron-capture element abundance [Sr/H] and [Ba/H] within the six observed SEGUE-1 stars in this study 
    (filled in red circles), one previously studied SEGUE-1 star (empty red circle), MW Halo stars (small black dots),
    and the other candidate stars (cyan, green, and blue markers). The light dotted line at [X/H] = 0 represents the abundance
    of the respective element within the sun and the bold dashed line represents the average abundance of the respective element
    within the observed SEGUE-1 stars.}
    \label{fig:carbon}
\end{wrapfigure}

In addition to confirming the age of the SEGUE-1 galaxy the authors also made some discoveries regarding chemical composition of early
stars. Figure ~\ref{fig:carbon} shows the carbon abundance [C/H] for the observed SEGUE-1 stars as well as other candidate stars and
MW Halo stars. We can see that 3 of the SEGUE-1 stars observed in this paper, as well as the one observed previously show enhanced levels
of carbon. These carbon enhanced stars are observed to be the the four lowest mass stars out of the seven SEGUE-1 stars and indicates the
importance of carbon in the enrichment process of early stars.

Additionally the authors observed a large range of iron abundance within the SEGUE-1 stars spanning over two orders of magnitude between
[Fe/H] = -1.4 to [Fe/H] = -3.8. this large range in combination with the relative consistency in metallicity of the stars indicates that
the distribution of iron within the intergalactic and interstellar medium was inhomogeneous in the early universe, around the time of
star formation within SEGUE-1

@@

Future research points to observing a larger portion of SEGUE 1 stars. The six stars that were observed in this paper, plus the 
star observed in a previous study, were deemed to be the brightest in the ultra faint dwarf galaxy with magnitudes of $\sim 19$ mag.
These seven SEGUE-1 stars were the only ones that scientists were able to capture sufficiently high resolution spectra for. These seven
only represent a small sample

\newpage
